---
title: "Can we go beyond simple predictors?"
author: "Rayhan Rashed"
date: "7/14/2020"
output: html_document
---
```{r, echo=FALSE}


packages <- c("ggplot2","plyr", "dplyr", "multcomp","MASS","knitr","DiagrammeR","effects","caret","boot","car")

#packages <- c("ggplot2", "readxl", "dplyr", "tidyr", "ggfortify", "DT", "reshape2", "knitr", "lubridate", "pwr", "psy", "car", "doBy", "imputeMissings", "RcmdrMisc", "questionr", "vcd", "multcomp", "KappaGUI", "rcompanion", "FactoMineR", "factoextra", "corrplot", "ltm", "goeveg", "corrplot", "FSA", "MASS", "scales", "nlme", "psych", "ordinal", "lmtest", "ggpubr", "dslabs", "stringr", "assist", "ggstatsplot", "forcats", "styler", "remedy", "snakecaser", "addinslist", "esquisse", "here", "summarytools", "magrittr", "tidyverse", "funModeling", "pander", "cluster", "abind")

librarian::shelf(packages,quiet = TRUE)

#read missing_regression.csv
# setwd("/Users/MBP/Documents/ElectronicWaste/")
# df=read.csv("temp.csv",stringsAsFactors = T)
# df  %>% head()
# describe(df)
# typeof(df)
# str(df)
# colnames(df)
# length(df)
# df$miss_another <- sub("N ", "N", df$miss_another)
# table(df$miss_another
#       )
# printsummary <- function(df) {
#   i <- 2
#   xtabs(~df[,i], data = df)
#   for (i in 2:length(df)) 
#   {
#     print(i)
#     print(xtabs(~df[,i], data = df))
#     i <- i + 1
#     
#   }  
# }
#creating a mutation script


mutation_df <- function(df) {
  #library(plyr)
  df$device_count_5_yr <- factor(
    df$device_count_5_yr
    ,
    levels = c("0", "1-2",
               "3-4", "4-6",
               "6-8", "8-10",
               "10-12", "12-")
  )
  #df$device_count_5_yr <- as.ordered(df$device_count_5_yr)
  mapvalues(df$device_count_5_yr,
            from = c("0", "1-2","3-4", "4-6","6-8", "8-10","10-12", "12-"),
            to = c("0", "2","4", "6","8", "10","12", "14")
            )
  
  df$device_count_5_yr <- as.numeric(df$device_count_5_yr)
  df$device_count_5_yr <- df$device_count_5_yr*2 -2  
  df$last_dumped_device <- relevel(df$last_dumped_device, "Smartphone")
  
  df$dump_within <- factor(df$dump_within,
                           levels = c("<1 mn", "<6 mn", "<1 yr", "<2 yr", "<4 yr", ">4 yr"))
  df$age <- as.ordered(df$age)
  df$dump_within <- as.ordered(df$dump_within)
  df$miss_another <- sub("N ", "N", df$miss_another)
  df$edu <- factor(df$edu,
                   levels = c("SSC","High School", "Bachelors","Masters","PhD"))
  df$edu <- factor(df$edu)
  
  
  #########checking-improving stepwise
  df$did_with_data_Y[df$did_with_data<=2]<-0 
  df$did_with_data_Y[df$did_with_data>=3]<-1
  df$did_with_device_econ[df$did_with_device<=2]<-1
  df$did_with_device_econ[df$did_with_device>=3]<-0
  #df$did_with_data <- factor()
  
  df$did_with_data_Y <- as.factor(df$did_with_data_Y)
  df$did_with_device_econ <- as.factor(df$did_with_device_econ)
  df <- dplyr::select(df,-c(did_with_data,did_with_device,X))
  
  # df$memory_dev[df$memory_dev=="N"] <- 0 
  # df$memory_dev[df$memory_dev=="Y"] <- 1
  # df$miss_another[df$miss_another=="N"] <- 0 
  # df$miss_another[df$miss_another=="Y"] <- 1
  levels(df$memory_dev) <- c(0,1)
  levels(df$miss_another) <- c(0,1)
  levels(df$miss_dev) <- c(0,1)
  
  df$bad_rep_exp <- relevel(df$bad_rep_exp,ref = "NC")
  #df$will_dev_rec[df$will_dev_rec==""] <- "NC"
  #df$will_dev_rec <- factor(df$will_dev_rec)
  df$will_dev_rec <- relevel(df$will_dev_rec,ref = "NC")
  
  #df$repair_try <- 1
  df$repair_try[df$self_try_No==1] <- 0
  df$repair_try[df$self_try_No==0] <- 1
  df$repair_try <- as.factor(df$repair_try)
  
  df$repair_succ[df$self_try_Success==1] <- 1
  df$repair_succ[df$self_try_Success==0] <- 0
  df$repair_succ <- as.factor(df$repair_succ)
  
  df$self_rep_combined[df$self_try_Success==1] <- "S"
  df$self_rep_combined[df$self_try_Failed==1] <- "F"
  df$self_rep_combined[df$self_try_No==1] <- "N"
  df$self_rep_combined <- factor(df$self_rep_combined)
  df$self_rep_combined <- relevel(df$self_rep_combined,"N")
  
 return(df)
}

create_code <- function(df) {
#  df$division.sum <- df$division
  contrasts(df$division) <- contr.sum(length(unique(df$division)))
  
  #df$age.sum <- df$age
  contrasts(df$age) <- contr.sum(length(unique(df$age)))
  contrasts(df$age) <- contr.sum(length(unique(df$age)))
  contrasts(df$last_dumped_device) <- contr.sum(length(unique(df$last_dumped_device)))
  contrasts(df$dump_within) <- contr.helmert(length(unique(df$dump_within)))
  
  return(df)
}

pack <- function(filename) {
  setwd("/Users/MBP/Documents/ElectronicWaste/")
  df=read.csv(filename,stringsAsFactors = T)
  #df=read.csv("temp.csv",stringsAsFactors = T)
  df <- mutation_df(df)
  #df <- rename_df(df)
  df <- create_code(df)
  return(df)
}

Generate_RoC <- function(full_model,null_model,df,outcome,direction) {
  library(ROCR)
  librarian::shelf(pROC,quiet = T)
  n <- nrow(df)
  print(n)
  trainingidx <- sample(1:n, 0.9 * n)
  train <- df[trainingidx,]
  test <- df[-trainingidx,]
  step_model <- NULL
  if (direction=="F") {
    step_model <- step(null_model, scope = list(lower = null_model, upper = full_model), direction = "forward", trace = FALSE)
    #print(step_model %>% summary())
    test$pred <- predict(step_model,test,type="response")
    test$real <- test[,outcome]
    
    train$pred <- predict(step_model,train,type="response")
    train$real <- train[,outcome]
    
  }
  else{
    step_model <-step(full.model,direction = "backward",trace = 0)
    #print(step_model %>% summary())
    
    test$pred <- predict(step_model,test,type="response")
    test$real <- test[,outcome]
    
    train$pred <- predict(step_model,train,type="response")
    train$real <- train[,outcome]
  }
  

  
  
  plot.roc(test$real,test$pred, col = "red", main="ROC Validation set",
           percent = TRUE, print.auc = TRUE)
  

}


```

```{r echo=FALSE}
#temp <- pack("temp.csv")
filename="temp.csv"
#filename="missing_regression.csv"
df <- pack(filename)

#view(df)
# i=0
# for (v in colnames(df)) {
#   print(v)
#   i=i+1
#   print(i)
# 
#   print(xtabs(~df[,v],data=df))
#   
#   if (v == "X" | v =="occupation" | v=="miss_dev") {
#     next
#   }
#   #model <- glm(miss_dev~df[,v],data = df,family = "binomial")
#   #print(summary(model))
#   
# }
#view(df)
#df[!complete.cases(df),]
#givenness <- read.csv(url("https://osf.io/q9e3a/download"))
#view(givenness)




#df %>% colnames()
#full.model <- update(full.model,~.)
# full.model <- update(full.model,~.-X-age-division)
attach(df)

full.model <- glm(formula = repair_try ~ gender + device_count_5_yr + dump_reason_break + 
                    slt_lack_tu + slt_lack_lang + slt_lack_parts + slt_lack_repairer + 
                    rprd_usage_chlng_fault + rpr_missing_trait_trust + rpr_missing_trait_gender + 
                    dev_tknto_rec_Y + dev_rec_chlng_hard_find + did_with_device_econ+device_count_5_yr:rprd_usage_chlng_fault+device_count_5_yr:dev_tknto_rec_Y+device_count_5_yr:did_with_device_econ+slt_lack_tu:dev_tknto_rec_Y+slt_lack_lang:rpr_missing_trait_gender+slt_lack_parts:rpr_missing_trait_gender+rpr_missing_trait_gender:dev_rec_chlng_hard_find+rpr_missing_trait_trust:dev_rec_chlng_hard_find+rpr_missing_trait_gender:did_with_device_econ,
                  family = binomial, data = df)

#full.model %>% summary()
```

This time we have added the following Interactions:

device_count_5_yr:rprd_usage_chlng_fault

device_count_5_yr:dev_tknto_rec_Y

device_count_5_yr:did_with_device_econ

slt_lack_tu:dev_tknto_rec_Y

slt_lack_lang:rpr_missing_trait_gender+slt_lack_parts:rpr_missing_trait_gender+rpr_missing_trait_gender:dev_rec_chlng_hard_find+rpr_missing_trait_trust:dev_rec_chlng_hard_find+rpr_missing_trait_gender:did_with_device_econ


```{r}
backward.model <- step(full.model,direction = "backward",trace = 0)

backward.model %>% summary()





```

$$
\begin{aligned}
\log\left[ \frac { P( repair\_try = 1 ) }{ 1 - P( repair\_try = 1 ) } \right] &= 0.08 - 0.77(gender_{Woman}) - 0.1(device\_count\_5\_yr)\ - \\
&\quad 0.39(dump\_reason\_break) + 0.61(slt\_lack\_tu) + 0.66(slt\_lack\_lang)\ + \\
&\quad 0.83(slt\_lack\_parts) + 0.65(slt\_lack\_repairer) - 2.09(rprd\_usage\_chlng\_fault)\ + \\
&\quad 0.73(rpr\_missing\_trait\_trust) - 0.55(gender_{rpr\_missing\_trait\_} \times rpr\_missing\_trait\_gender) - 1.44(dev\_tknto\_rec\_Y)\ - \\
&\quad 1.06(dev\_rec\_chlng\_hard\_find) + 0.75(did\_with\_device\_econ_{1}) + 0.29(device\_count\_5\_yr \times rprd\_usage\_chlng\_fault)\ + \\
&\quad 0.31(device\_count\_5\_yr \times dev\_tknto\_rec\_Y) + 1.61(slt\_lack\_tu \times dev\_tknto\_rec\_Y) + 1.69(gender_{rpr\_missing\_trait\_} \times rpr\_missing\_trait\_gender_{did\_with\_device\_econ1} \times did\_with\_device\_econ_{rpr\_missing\_trait\_gender})\ + \\
&\quad \epsilon
\end{aligned}
$$


The AIC Value was Initially 436.
After Stepwise Regression, it came down to 395.
***After Adding the Interaction elements, it is now 385***

The 10 fold cross validation accuracy is below:
```{r}
cross_validated_model <- boot::cv.glm(df,glmfit = backward.model,K = 10)
print((1-cross_validated_model$delta[1])*100)

```
Lets also look at the ROC curve for the the fitted logistic regression model: ***(A better fit than model without interaction)***

```{r}
null.model <- glm(repair_try~1,family = binomial(),data = df)
Generate_RoC(full_model = full.model,null_model = null.model,df = df,direction = "B",outcome = "repair_try")

```
With a good fit in the model, lets diagnosis our model parameters for multicolineariy. If the ***VIF*** (Variance Inflation Factor) is $>10$ for any predictor, we might be in trouble.

```{r}
cat("MIN IVF: ",min(vif(backward.model)))
cat("MAX IVF: ",max(vif(backward.model)))
cat("MEAN IVF: ",mean(vif(backward.model)))
        
```

Values $>0$ means odd$>1$  So, that accounts more for YES than NO.



***device_count_5_yr : fear of faulty device ***        


***device_count_5_yr: device ever taken to RECYCLER ***     


***lack_of_tutorial : device ever taken to RECYCLER ***     


***gender_adversary_of_repairers :Have you did anything economic with your device***

Lets look at the effects plot to better understand the individual effects of each predictor:

```{r echo=FALSE}

#librarian::shelf(effects)

for (n in c(
"gender"
,"did_with_device_econ"
#,"device_count_5_yr"
,"dump_reason_break"
,"slt_lack_tu"
,"slt_lack_lang"
,"slt_lack_parts"
,"slt_lack_repairer"
,"rprd_usage_chlng_fault"
,"rpr_missing_trait_trust"
,"rpr_missing_trait_gender"
#,"dev_tknto_rec_Y"
,"dev_rec_chlng_hard_find"
)){
  #print(n)
  print(plot(effects::predictorEffect(n,backward.model)))
}

```


